---
title: "Data Science Methods for Economics and Finance 871 Exam" 
author: "Talyah Greyling (23761067)" 
output:
    md_document:
    variant: markdown_github
---

# PURPOSE: 

This readme is located in my repository for the Data Science Methods for Economics and Finance 871 Exam. 
The repository contains all of my code, figures, tables, and write-ups for the exam. 
There are a total of five questions & each question has its own folder with an accompanying code and data folder.
 

```{r create folders, eval = FALSE}

#The project was created by copying the file path for my repository file (C:/Users/Talyah Greyling/Documents/1) Meesters/1) Data Science 871/Data-Science-Exam) and then using fmxdat::make_project(ProjNam = "23761067"). 

#This code was used to create the question folders: 
location <- "C:/Users/Talyah Greyling/Documents/1) Meesters/1) Data Science 871/Data-Science-Exam"
Texevier::create_template(directory = location, template_name = "Question1")
Texevier::create_template(directory = location, template_name = "Question2")
Texevier::create_template(directory = location, template_name = "Question3")
Texevier::create_template(directory = location, template_name = "Question4")
Texevier::create_template(directory = location, template_name = "Question5")

```

#QUESTION 1:

##Code used for figures and tables: 

```{r setup, echo = FALSE, output = TRUE}

rm(list = ls())     # clean environment
gc()    # garbage collection 

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

library(pacman)
p_load(tidyverse, lubridate)

# Source in functions:
list.files('Question1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

```

### Data

The unzipped data files are in their respective question folders.

### Question 1

#### Loading the data

```{r}
# See why the parameter Datroot was useful now?
datcolat <- Data_Collating(Datroot = "Question1/Data/Happy/")

```







