---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "What makes us happy?"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Nico Katzke^[__Contributions:__  \\newline _The authors would like to thank the World Happiness survey for showing us what happiness is._]"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Satrix, Cape Town" # First Author's Affiliation
Email1: "nfkatzke\\@gmail.com" # First Author's Email address

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  This article aims to discuss what makes us happy. This is a suggested solution to question 1.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

datcolat <- Data_Collating(Datroot = "Data/Happy/")


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

You are welcome to add some sort of an introduction here. Spend 5 minutes detailing the purpose here, e.g.

Look at the README.txt file and maybe give some background - especially also in understanding the definition of the variables.

Notice that for the below plots I created a parameters to play around with xaxis labels.

```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Happiness Ladder.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

  # Source the plot with a function, and then print it as below.
    # Going through the function, you will note that I'm able to source other functions in the code folder in these functions too.
# That's the beauty of centralizing your functions and loading it in the top.

  g <-
    Error_bar_plot(datcolat, xaxis_size = 5, xaxis_rows = 3)
    
g

```

\newpage

Let's start a newpage here, just because. 

```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Happiness Ladder.\\label{Figure2}", fig.ext = 'png', fig.height = 6, fig.width = 6}

  # Why not make titles and subtitles parameters?

  g <-
    Barplot_breakdown_Happy_Contributors(datcolat, Title = "Barplot making up the ladder", Subtitle = "Look at the colours - wow.", xaxis_size = 5, xaxis_rows = 3)
    
g

```

Try sprucing up the above figures even more, as well as adding some interpretation of the figures here.

As you can see from Figure \ref{Figure1}, happiness is not perfectly correlated with life expectancy. Maybe posit some theory here and reference a paper to show that you can do this as well. If you do that, just keep in the bibliography information of course - as I didn't cite anyone here, I omitted it.

